---
title: "ds4owd - capstone project report"
subtitle: "faecal sludge analysis"
author: "Rainbow Train"
format: html
execute: 
  echo: true
  warning: false
editor: visual
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(gt)
```

 	The report renders without errors to HTML format and contains at least four chapters of heading level 1 that are named: Introduction, Methods, Results, Conclusions.

# Introduction

The goal of this project is to analyse samples from a feacal sludge characterization study. Samples were collected in ... between ...

```{r}
sludge <- read_csv(file = here::here("data/processed/faecal-sludge-analysis.csv"))
```

# Methods

# Results

```{r}

tbl_summary_users_ts <- sludge |> 
  filter(!is.na(users)) |> 
  group_by(location, system) |> 
  summarise(
    count = n(),
    mean_users = mean(users),
    sd_users = sd(users),
    median_users = median(users),
    mean_ts = mean(ts),
    sd_ts = sd(ts),
    median_ts = median(ts)
  )

```

@tbl-summary-users-ts shows ...

```{r}
#| label: tbl-summary-users-ts
#| tbl-cap: Summary statistics for number of users and total solids (mg/L) by sample location and sanitation system. 

tbl_summary_users_ts |> 
  ungroup() |> 
  gt() |> 
  fmt_number(columns = mean_users:median_users, decimals = 0) |> 
  fmt_number(columns = mean_ts:median_ts, decimals = 1)
```



# Conclusions

# References
